D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-03 ootavacuous.tex
"Interthread Communication": Reword
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Next, definitions:
\begin{description}
\item[coe]
	Coherence-order (external), which connects a store to any other store
	for the same object that comes later in the object's
	modification order, i.e., that overwrites either the first store's
	value or some later value.
\item[fre]
	From-read (external), which connects a load to any store for
	the same object that overwrites either the value that the load
	returned or some later value.
\item[rfe]
	Reads-from (external), which connects a store to any load from
	the same object that returns the value stored.
	(Note: This means that the load retrieves the information
	written by the store, as opposed to retrieving the information
	from a different store that happened to write the same value.)
\end{description}

@@

Thirdly, Figure~\ref{fig:ITC Diagram for coe, fre, and rfe} illustrates
the coe, fre, fri, and rfe links for four threads with time advancing
from the top to the bottom of the figure.  Start with coe: Even though
Thread~1's store is later in global time than that of Thread~0, the
Thread~1 store comes first in \co{x}'s modification order, then Thread-0's
store, then those of Threads~2 and ~3.
There is thus a coe link from Thread~1's store to every other store,
from Thread~0's store to those of Threads~2 and~3, and from Thread~2's
store to that of Thread~3.
This situation can occur due to the initial placement and subsequent
movement of cache lines.

Thread~3's load reads the value written by Thread~0's store, so there is
an rfe link from that store to that load.  In addition there is an fre link from
the load to Thread~2's store and an fri link to Thread~3's later store.
Note that the fre link goes backwards in time.

>>>>

Next, definitions:
\begin{description}
\item[coe]
	Coherence-order (external), which connects a store to any other store
	to the same object that comes later in the object's
	modification order, i.e., that overwrites either the first store's
	value or some later value.
\item[fre]
	From-read (external), which connects a load to any store to
	the same object that overwrites either the value that the load
	returned or some later value.
\item[rfe]
	Reads-from (external), which connects a store to any load from
	the same object that returns the value stored.
	(Note: This means that the load retrieves the information
	written by the store, as opposed to retrieving the information
	from a different store that happened to write the same value.)
\end{description}

@@

Thirdly, Figure~\ref{fig:ITC Diagram for coe, fre, and rfe} illustrates
the coe, fre, fri, and rfe links for four threads with time advancing
from the top to the bottom of the figure.  Start with coe: Even though
Thread~1's store is later in global time than that of Thread~0, the
Thread~1 store comes first in \co{x}'s modification order, then Thread~0's
store, then those of Threads~2 and~3.
There is thus a coe link from Thread~1's store to every other store,
from Thread~0's store to those of Threads~2 and~3, and from Thread~2's
store to that of Thread~3.
This situation can occur due to the initial placement and subsequent
movement of cache lines.

Thread~3's load reads the value written by Thread~0's store, so there is
an rfe link from that store to that load.  In addition there is an fre link from
the load to Thread~2's earlier store and an fri link to Thread~3's later store.
Note that the fre link goes backwards in time.
